Peer Assessment 1  
=====================
assignment by Jaeyoon

###Loading and preprocessing the data  
Codes below load data, and process it into a format suitable for analysis.
```{r loading and preprocessing,warning=FALSE}
data<-read.table("activity.csv",header=TRUE,sep=",")
library(date) # execute code [install.packages("date")] if you haven't installed packages "date" 
data$date<-as.Date(data$date) # transform data's class into 'date'
```

###Q1. What is mean total number of steps taken per day(missing values ignored)
- Codes below make subset for analysis.
```{r q1_1}
subset_day<-aggregate(data$steps,by=list(data$date),FUN=sum) # makes subset which counts steps by(per) date 
head(subset_day) # shows head of subset
```
- Histogram of the total number of steps taken each day
```{r q1_2,results='asis'}
hist(subset_day[[2]],main="Total number of steps taken each day",xlab="sum of steps") # makes histogram
```  

- Mean and median total number of steps taken per day
```{r q1_3}
mean<-mean(subset_day[[2]],na.rm=TRUE)
median<-median(subset_day[[2]],na.rm=TRUE)
```
mean : **`r mean`** / median : **`r median`**
  
###Q2. What is the average daily activity pattern?
- Codes below make subset for analysis.
```{r q2_1}
subset_itv<-aggregate(data$steps,by=list(data$interval),FUN=mean,na.rm=TRUE) # makes subset which average(mean) steps by(per) intervals
head(subset_itv) # shows head of subset
```
- Plot of the average daily activity pattern
```{r q2_2,results='asis'}
plot(subset_itv,main="Average daily activity pattern",type="l",xlab="5-minute interval",ylab="average number of steps taken, averaged across all days") # makes plot
max_row<-subset_itv[which.max(subset_itv[[2]]),1] # finds interval contains maximum number of steps
points(max_row,max(subset_itv[[2]]),pch=22) # indicate maximum value
```

The interval which contains maximum number of steps is **`r max_row`** 

###Imputing missing values
1. Total number of missing values in the dataset
```{r imputting_1}
nadata<-is.na(data[1])
n_nadata<-sum(nadata) # extract and count missing values
```
numbers of missing values : **`r n_nadata`**  
  
2&3. Strategy for filling in all of the missing values in the dataset
  -> use the mean for the interval
```{r imputting_2}
colnames(subset_itv)<-c("interval","steps_mean")
new_data<-merge(data,subset_itv,by="interval")
new_data$steps[is.na(new_data$steps)]<-new_data$steps_mean[is.na(new_data$steps)] # replace NA value with corresponding(same interval mean) value
head(new_data) # show head of new data(filled)
```  
  -> new dataset(missing data filled)
  
4. Histogram/mean and median of the total number of seps taken each day
```{r imputting_3,results='asis'}
new_subset_day<-aggregate(new_data$steps,by=list(new_data$date),FUN=sum)
hist(new_subset_day[[2]],main="Total number of steps taken each day",xlab="sum of steps") # makes histogram
new_mean<-mean(new_subset_day[[2]])
new_median<-median(new_subset_day[[2]])
```  
mean : **`r new_mean`** / median : **`r new_median`**
mean value isn't changed, with equivalent median and variation decreasing

###Q3. Are there differneces in activity patterns between weekdays and weekends?
1. Codes make new factor variable (weekday/weekend)
```{r}
wdwe<-factor(weekdays(new_data$date)) # listed by '~days'
levels(wdwe) # show factors(in Korean)
levels(wdwe)<-c("weekday","weekday","weekday","weekday","weekend","weekend","weekday") # merge factors
new<-cbind(new_data,wdwe) # mergy factors into data
```
2. Make a panel plot
```{r}
new_subset_itv<-aggregate(new$steps,by=list(new$wdwe,new$interval),FUN=mean,na.rm=TRUE)
colnames(new_subset_itv)<-c("weekday","interval","steps")
library(lattice)
xyplot(new_subset_itv$steps~new_subset_itv$interval|new_subset_itv$weekday,layout=c(1,2),type="l",xlab="Interval",ylab="Number of steps")
```